\documentclass[a4paper,10pt]{article}

\usepackage[a4paper,margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[T1]{fontenc}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    {\LARGE \textbf{Stanislav Romanov}} \\
    \smallskip
    Berlin, Germany \\
    \texttt{stanislavromanov.com} | \texttt{stanislav.romanov@outlook.com} | \texttt{+49 174 8970750 (WhatsApp)} \\
\end{center}

\section{Summary}
Experienced software engineer with a strong background in backend and frontend development. Expertise in designing secure, scalable, and high-performance systems, mentoring teams, and leading engineering projects.

\section{Key Skills}
\begin{itemize}[noitemsep,topsep=0pt]
    \item \textbf{Backend:} JavaScript, TypeScript, Node.js, C\#, PHP, RESTful APIs, microservices, serverless computing, test-driven development, CI/CD.
    \item \textbf{Frontend:} JavaScript, TypeScript, React, Angular, Next.js, Tailwind CSS, Material UI, SSR, SSG, performance optimization.
    \item \textbf{Databases:} SQL and NoSQL knowledge, database optimization, horizontal scaling.
    \item \textbf{AI/ML:} OpenAI APIs, Stable Diffusion, Hugging Face, AI integrations.
    \item \textbf{Other:} DevOps, Docker, cloud computing, security best practices.
\end{itemize}

\section{Work Experience}
\textbf{        }
\textbf{        }
\textbf{}
\textbf{Head of Engineering} \hfill 2016 -- 2024 \par
\textbf{Whitewall Media GmbH, Frechen, Germany (Remote)} \par
\begin{itemize}[noitemsep,topsep=0pt]
    \item Led engineering efforts for both front-end and back-end solutions, ensuring high performance and robust security.
    \item Architected and developed a high-performance Angular-based web application with a Java API backend.
    \item Mentored junior developers and coordinated cross-functional teams to meet project deadlines.
    \item Implemented microservices and containerization strategies to improve scalability.
\end{itemize}
\vspace{6pt}

\textbf{Software Engineer} \hfill 2014 -- 2016 \par
\textbf{Spotcap (Rocket Internet), Berlin, Germany} \par
\begin{itemize}[noitemsep,topsep=0pt]
    \item Migrated a legacy Symfony2 monolith to a microservices-based Node.js architecture.
    \item Developed and maintained a financial loan service processing millions of euros monthly.
    \item Enforced strict security standards and optimized API performance.
    \item Collaborated with multidisciplinary teams to streamline development processes.
\end{itemize}
\vspace{6pt}

\textbf{Senior Backend Developer} \hfill 2013 -- 2014 \par
\textbf{Transmessenger, Toronto, Canada} \par
\begin{itemize}[noitemsep,topsep=0pt]
    \item Designed and built a multi-tenant CRM with customizable features and secure API endpoints.
    \item Implemented role-based access control to handle millions of records and complex queries.
    \item Optimized database performance to support high-volume operations.
\end{itemize}
\vspace{6pt}

\textbf{Web Developer} \hfill 2011 -- 2013 \par
\textbf{DNX Marketing, London, UK (Remote)} \par
\begin{itemize}[noitemsep,topsep=0pt]
    \item Developed websites and mobile applications for major clients including Cisco, Intel, and SAP.
    \item Built fast and responsive web applications using Angular, PHP, and Cordova.
    \item Enhanced user engagement through performance optimizations and responsive design.
\end{itemize}
\vspace{6pt}

\textbf{Web Developer} \hfill 2009 -- 2011 \par
\textbf{OR Mebeles, Riga, Latvia} \par
\begin{itemize}[noitemsep,topsep=0pt]
    \item Created a custom eCommerce platform, increasing company revenue by 5x.
    \item Developed scalable solutions in C\# and MSSQL.
    \item Integrated payment gateways and implemented dynamic product catalogs.
\end{itemize}
\vspace{6pt}

\section{Other Projects}
\begin{itemize}[noitemsep,topsep=0pt]
    \item \textbf{ETIQL (2024):} Developed ETIQL’s Shopify store, implementing designs with Liquid.
    \item \textbf{NARR8 (2024):} Built an interactive story designer with Firebase, React, and OpenAI.
    \item \textbf{Lumas (ArtStream) (2023):} Built ArtStream’s backend with AWS Lambda, S3, and DynamoDB.
    \item \textbf{DKNY (2013):} Built DKNY’s eCommerce site with WordPress and WooCommerce.
    \item \textbf{SAP (2012):} Built an AngularJS marketing site for SAP, showcasing data in sports.
    \item \textbf{Cisco (2012):} Built a PHP/WordPress marketing site for Cisco’s collaboration event.
    \item \textbf{Autodesk (2011):} Built a Cordova-based mobile app for Autodesk showcasing technologies.
    \item \textbf{Axis (2011):} Built a marketing site for Axis, showcasing systems and cameras.
\end{itemize}

\section{Education}
\textbf{Engineering Technical College of Riga}, Riga, Latvia \\
Concentration: Computer Science

\section{Honors and Awards}
\begin{itemize}[noitemsep,topsep=0pt]
    \item \textbf{New Professional 2012 (1st Place)} – Built a web banking prototype using .NET in a 3-day competition sponsored by Microsoft.
    \item \textbf{Gratitude Diploma, RTK} – Recognized for active contributions to the college community.
\end{itemize}

\end{document}
